### 2014-10-31 fundamentals/qa.tex
mostly gls and \Cyclus

Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
tests. Sufficient unit tests are required for any proposed change to the \Cyclus
code base. Currently \Cyclus implements over 450 unit tests and \Cycamore has 
85.  These cover approximately 65\% of their respective code bases. This number 
is expected to grow over time.

@@

Version control is the history-preserving mechanism by which the provenance of 
a code is recored. Cyclus uses a well-established tool called git 
\cite{software_freedom_conservancy_git_2014}
for this purpose. Git is currently the most popular utility in the recent wave
of \emph{distributed version control}. Briefly stated, this means that every 
user has a complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
Though there and many praises and criticisms of git, one 
feature that the tool performs exceptionally well is the notion of code branches.
These are distinct pathways in the history that branch out of a mainline source
tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
branches may exist at all point in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an 
accompanying message. Thus 
it is possible for \Cyclus to accurately replay the entirety of who did what to the
code when.

Cyclus uses a strategy known as \emph{git flow} 
\cite{kalliamvakou_code-centric_2014} 
to manage topical branches where individuals develop code, the mainline development
branch (simply known as develop), and the stable branch (called master).
In addition to these rules and delineation, \Cyclus also imposes rules on 
when it is acceptable from a quality control standpoint to merge code from 
the personal topical branches into develop. All software at this stage 
must have sufficient and passing tests and comprehensive documentation. Without
these core pieces proposed changes are not allowed into \Cyclus. A schematic of 
the development stages between reporting a bug and merging the fix is shown in 
Figure \ref{fig:gitprocess}.

@@

In any multi-person software project, there is a tension between how individuals
wish to write code. Every person tends to have their own custom style. To remedy this
coding style guides are the software analogy to the natural language ones, 
such as the Chicago Manual of Style. Cyclus strictly enforces the use of the 
Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
This means that all developers of \Cyclus nominally write \Cyclus code in the same 
way.  This homogenization may be a hurdle to new developers but ultimately 
makes the it much more legible. Adoption of a single style guide also settles
timeless arguments over what style is `the best.' Having only one means that 
there is a common enemy for all developers to dislike equally.

@@

Continuous integration (CI) the idea that software should be tested and validated 
as it is being developed, rather than as a final stage in a longer development 
cycle.  Under CI every pull request is tested independently immediately after 
it is proposed. Such tests should be run on all officially supported platforms. 
Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.

>>>>

\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
tests. Sufficient unit tests are required for any proposed change to the \Cyclus
code base. Currently \Cyclus implements over 450 unit tests and \Cycamore has 
85.  These cover approximately 65\% of their respective code bases. This number 
is expected to grow over time.

@@

Version control is the history-preserving mechanism by which the provenance of 
a code is recored. \Cyclus uses a well-established tool called git 
\cite{software_freedom_conservancy_git_2014}
for this purpose. Git is currently the most popular utility in the recent wave
of \emph{distributed version control}. Briefly stated, this means that every 
user has a complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
Though there and many praises and criticisms of git, one 
feature that the tool performs exceptionally well is the notion of code branches.
These are distinct pathways in the history that branch out of a mainline source
tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
branches may exist at all point in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an 
accompanying message. Thus 
it is possible for \Cyclus to accurately replay the entirety of who did what to the
code when.

\Cyclus uses a strategy known as \emph{git flow} 
\cite{kalliamvakou_code-centric_2014} 
to manage topical branches where individuals develop code, the mainline development
branch (simply known as develop), and the stable branch (called master).
In addition to these rules and delineation, \Cyclus also imposes rules on 
when it is acceptable from a quality control standpoint to merge code from 
the personal topical branches into develop. All software at this stage 
must have sufficient and passing tests and comprehensive documentation. Without
these core pieces proposed changes are not allowed into \Cyclus. A schematic of 
the development stages between reporting a bug and merging the fix is shown in 
Figure \ref{fig:gitprocess}.

@@

In any multi-person software project, there is a tension between how individuals
wish to write code. Every person tends to have their own custom style. To remedy this
coding style guides are the software analogy to the natural language ones, 
such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the 
Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
This means that all developers of \Cyclus nominally write \Cyclus code in the same 
way.  This homogenization may be a hurdle to new developers but ultimately 
makes the it much more legible. Adoption of a single style guide also settles
timeless arguments over what style is `the best.' Having only one means that 
there is a common enemy for all developers to dislike equally.

@@

\emph{\acrfull{CI}} the idea that software should be tested and validated 
as it is being developed, rather than as a final stage in a longer development 
cycle.  Under \gls{CI} every pull request is tested independently immediately after 
it is proposed. Such tests should be run on all officially supported platforms. 
\Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.
